Summary Statistics

### 2025-02-26 extensive_tests/draft-sumstat-vignette.Rmd
Updating functions to compute freq of sites changing at each methylation structure

>>>>

- `freqSites_cherryMethDiff(tree,data)`. The function first validates the tree structure and extracts pairwise distances between cherry tips with `get_cherryDist`. It then validates the input data and counts half and full methylation differences for each cherry at each structure using `countSites_cherryMethDiff`. Finally, it normalizes these (half and full) counts by the number of sites per structure to compute frequencies. .

- `get_siteFChange_cherry(tree,data)`. Uses `freqSites_cherryMethDiff(tree,data)` and then computes the frequency of sites with any change of methylation state (full or half) for each cherry at each genomic structure.

```{r}
# Set example tree and methylation data
tree <- "((a:1.5,b:1.5):2,(c:2,d:2):1.5);"
data <- list(
    list(rep(1,10), rep(0,5), rep(1,8)), # tip a
    list(rep(1,10), rep(0.5,5), rep(0,8)), # tip b
    list(rep(1,10), rep(0.5,5), rep(0,8)), # tip c
    list(c(rep(0,5), rep(0.5, 5)), c(0, 0, 1, 1, 1), c(0.5, 1, rep(0, 6)))) # tip d

get_siteFChange_cherry(tree = tree, data = data)
```
